Generation of Variation and Mean Fitness Increase: \\ Necessity is the Mother of Genetic Invention

### 2017-11-28 ms.tex
remove another modifier statement

Therefore, increased transition from types in $K$ will increase the stable population mean fitness if the average fitness of individuals descended from types in $K$ is below the stable population mean fitness.
For example, \citet[Appendix~B]{Ram2012} considered individuals that are grouped by the number of their accumulated mutant alleles, $k$ (see \nameref{sec:mut_model_2}), 
and a modifier allele that increases the mutation rates in individuals with at least $\pi$ mutant alleles.
According to Eq.~\ref{eq:mfp_sign_threshold}, this modifier will increase the stable population mean fitness if individuals with $\pi$ or more mutant alleles have below-average fitness.

>>>>

Therefore, increased transition from types in $K$ will increase the stable population mean fitness if the average fitness of individuals descended from types in $K$ is below the stable population mean fitness.
For example, \citet[Appendix~B]{Ram2012} considered individuals that are grouped by the number of their accumulated mutant alleles, $k$ (see \nameref{sec:mut_model_2}), 
and the effect of increasing the mutation rate in individuals with at least $\pi$ mutant alleles.
According to Eq.~\ref{eq:mfp_sign_threshold}, this will result in increased stable population mean fitness if individuals with $\pi$ or more mutant alleles have below-average fitness.
